Main Analysis for Biracial Grade Retention Project

### 2022-09-05 analysis/analysis_main.Rmd
Add ending time stamp to main analysis
Remove warnings in main analysis; save model summaries; description of desc stats

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval=TRUE)
library(here)
source(here("analysis","check_packages.R"))
source(here("analysis","useful_functions.R"))
load(here("analysis","output","acs.RData"))
```

@@

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
library(here)
source(here("analysis","check_packages.R"))
source(here("analysis","useful_functions.R"))
load(here("analysis","output","acs.RData"))
```

@@

The results clearly show substantial differences in the grade retention of single race groups. Indigenous students have the highest grade retention at 7.9%, while Asian students have the lowest at 2.6%. Whites are also relatively low at 3.5%, while Latinos and Asians have similar and higher grade retention probabilities of 5.1% and 5.5%, respectively. Biracial groups also vary substantially, but I will develop better ways of understanding their placement graphically below. These numbers also make no adjustment for important covariates.

The biracial groups are generally a little bit younger than the monoracial groups, although the monoracial groups also vary in age a bit. Its possible this may bias the grade retention percentages down a bit, but the differences seem quite minor.

@@

```{r save-models}
model0_summary <- summary(model0)
model1_summary <- summary(model1)
model2_summary <- summary(model2)
model3_summary <- summary(model3)
model4_summary <- summary(model4)
save(model0_summary, model1_summary, model2_summary, model3_summary,
     model4_summary, file=here("analysis","output","model_summaries.RData"))
```
